---
title: "Day 4 Interactive"
format: html
editor: visual
---

## Functions

#### Make a function that doubles  a value

```{r}
double_value <- function(my_dollars){
  print(2*my_dollars)
}
  

double_value(3)
```

Can try this with vectors

```{r}
monthly_income <- c(42.5,61.75,89.5)

double_value(monthly_income)
```

#### Create a function that returns an awesome restaurant name given a cool animal and favorite food

```{r}
name_restaurant <- function(animal,food){
  print(paste(animal,food))
}

name_restaurant("Cat","pizza")
```

#### Given temperature in degrees Fahrenheit, write a function that converts it to Celsius

```{r}
convert_f_to_c <- function(f_temp){
  celsius_temp <- (f_temp -32)*5/9 
  print(celsius_temp)
}

convert_f_to_c(86)
```

#### Create a function that given inputs of age and hometown, returns "I am \_\_ years old, and I'm from \_\_"

```{r}
age_hometown <- function(age,hometown){
  print(paste("I am", age, "years old, and I'm from",hometown))
}

age_hometown(25,"Brooklyn")
```

In R this is already stored and will present it without the need of print

```{r}
double_value2 <- function(dollars){
  dollars*2
}

double_value2(10)*0.08
```

For python

statments and return statements

Print:"show me "

Return: store this aso i can use it later
